\documentclass[10pt, letterpaper]{article}

% Packages:
\usepackage[
    ignoreheadfoot,
    top=2 cm,
    bottom=2 cm,
    left=2 cm,
    right=2 cm,
    footskip=1.0 cm,
]{geometry}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\definecolor{primaryColor}{RGB}{0, 0, 0}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=primaryColor
}
\usepackage{paracol}
\usepackage{ifthen}
\usepackage{needspace}

\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\columnsep}{0.15cm}
\pagenumbering{gobble}

\titleformat{\section}{\needspace{4\baselineskip}\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]

\titlespacing{\section}{-1pt}{0.3 cm}{0.2 cm}

\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}

\begin{document}

\begin{center}
    \textbf{\LARGE CHARVITHA S KOTA}\\
    Tallahassee, FL | \href{mailto:charvithakota@gmail.com}{charvithakota@gmail.com} | +1(862)-357-5964 | \href{https://www.linkedin.com/in/charvitha-kota}{linkedin.com/in/charvitha-kota}
\end{center}

\section{Education}
\textbf{Florida State University}, Tallahassee, FL \hfill 08.2023 -- 05.2025\\
Master of Science in Information Technology\\
\textbf{Jawaharlal Nehru Technological University}, Kakinada, India \hfill 06.2015 -- 05.2019\\
Bachelor of Technology in Information Technology

\section{Work Experience}
\textbf{JIO Pvt Ltd} | Data and System Analyst (Product Owner Focus) \hfill Hyderabad, India | 12.2021 -- 08.2023\\
\begin{itemize}[noitemsep]
    \item Led 4 major product development initiatives resulting in 15\% improvement in operational efficiency.
    \item Managed a product backlog of 200+ items and reduced feature delivery time by 30\%.
    \item Conducted system analysis using SQL across 5 databases, improving data accuracy by 25\%.
    \item Implemented Agile methodologies leading to 40\% faster sprint velocity and 20\% reduction in bug reports.
    \item Facilitated 12+ cross-functional team meetings weekly, coordinating between multiple teams.
    \item Reduced system downtime by 35\% through proactive monitoring.
\end{itemize}

\textbf{Amazon} | Product Analyst \hfill Hyderabad, India | 07.2020 -- 07.2021\\
\begin{itemize}[noitemsep]
    \item Managed product backlog of 150+ items and achieved 95\% on-time feature delivery rate.
    \item Created and maintained 6-month product roadmaps, delivering 25+ new features.
    \item Developed 8 customized Power BI dashboards, increasing stakeholder visibility by 60\%.
    \item Conducted 24 user research sessions with 100+ participants.
    \item Reduced customer complaint tickets by 45\% through targeted improvements.
\end{itemize}

\textbf{Tech Mahindra Pvt Ltd} | Data Analysis Intern \hfill Hyderabad, India | 08.2019 -- 07.2020\\
\begin{itemize}[noitemsep]
    \item Analyzed data from 50,000+ user sessions to optimize product performance.
    \item Created 5 automated reporting workflows, saving 10+ hours per week.
    \item Improved data accuracy by 40\%.
    \item Contributed to 3 major product releases.
\end{itemize}

\section{Projects}
\textbf{Enhanced Product Lifecycle Management for ITSM}
\begin{itemize}[noitemsep]
    \item Led product development for platform serving 75,000+ end users.
    \item Defined and tracked 15 key product metrics, achieving 92\% of target KPIs.
    \item Conducted UAT testing with 50+ users.
    \item Reduced average ticket resolution time by 35\%.
    \item Achieved 98\% system reliability.
\end{itemize}

\textbf{Customer-Centric Data Platform Optimization}
\begin{itemize}[noitemsep]
    \item Managed backlog of 100+ items.
    \item Developed 30+ detailed user stories.
    \item Implemented customer feedback system, improving satisfaction scores by 40\%.
    \item Reduced data processing time by 60\%.
    \item Coordinated with engineering teams across time zones.
\end{itemize}

\section{Technical Skills}
\begin{itemize}[noitemsep]
    \item \textbf{Product Management}: Requirements Gathering, Sprint Planning, Backlog Management, UAT Testing.
    \item \textbf{Tools}: JIRA, Confluence, Power BI, Tableau, Microsoft Office Suite.
    \item \textbf{Technical Skills}: SQL, Python, R, Agile \& Scrum Methodologies.
    \item \textbf{Soft Skills}: Stakeholder Collaboration, Analytical Thinking, Communication, Problem-Solving.
\end{itemize}

\end{document}
